Empirical Measures Template

### 2021-10-06 StateOfPractice/DomainMeasurements/LBM-Peter/Peter-Notes-SolutionDescriptions.tex
Rearrange domain measurement reports to have more consistent naming and locations

	\item ch4-project\\
	\href{https://github.com/SoftwareImpacts/SIMPAC-2019-1}{https://github.com/SoftwareImpacts/SIMPAC-2019-1}\\  
	Found using Google search.\\
	Eulerian-Lagrangian fluid dynamics platform
	A general purpose Lattice-Boltzmann code for fluid-dynamics simulations. It includes :
	fluid dynamics (with several volume forcing terms for Channel flow, Homogeneous Isotropic Turbulence, buoyancy)
	temperature dynamics (advection, diffusion , sink/source or reaction terms)
	phase change (enthalpy formulation for solid/liquid systems)
	scalar transport (same functionalities as temperature)
	lagrangian dynamics (tracers, heavy/light and active point-like particles; non-shperical Jeffery rotation, gyrotaxis)
	large eddy simulation (Smagorinsky, Shear Improved Samgorinsky with Kalman Filter)

@@

	\item fvLBM
	\\
	\href{https://github.com/zhulianhua/fvLBM}{https://github.com/zhulianhua/fvLBM}
	\\
	Found using Google search.\\
	finite volume lattice Boltzmann method

@@

	\item LBDEMcoupling-public
	\\
	\href{https://github.com/ParticulateFlow/LBDEMcoupling-public}{https://github.com/ParticulateFlow/LBDEMcoupling-public}
	\\
	Found using Google search.\\
	Coupling between the Lattice-Boltzmann code Palabos and the DEM code LIGGGHTS

>>>>

\item ch4-project\\
\href{https://github.com/ecalzavarini/ch4-project}{https://github.com/ecalzavarini/ch4-project}\\  
Found using Google search.\\
Eulerian-Lagrangian fluid dynamics platform
A general purpose Lattice-Boltzmann code for fluid-dynamics simulations. It includes :
fluid dynamics (with several volume forcing terms for Channel flow, Homogeneous Isotropic Turbulence, buoyancy)
temperature dynamics (advection, diffusion , sink/source or reaction terms)
phase change (enthalpy formulation for solid/liquid systems)
scalar transport (same functionalities as temperature)
lagrangian dynamics (tracers, heavy/light and active point-like particles; non-shperical Jeffery rotation, gyrotaxis)
large eddy simulation (Smagorinsky, Shear Improved Samgorinsky with Kalman Filter)

@@

\item fvLBM
\\
\href{https://github.com/zhulianhua/fvLBM}{https://github.com/zhulianhua/fvLBM}
\\
Found using Google search.\\
A finite volume lattice Boltzmann method solver implementated on OpenFOAM.

@@

### 2021-10-06 StateOfPractice/DomainMeasurements/LBM-Peter/Report/Report.tex
Rearrange domain measurement reports to have more consistent naming and locations

\thesistitle
	{\MakeUppercase{\fulltitle}}
	{\MakeUppercase{\authorname}.}
	{Master of Engineering in Computing and Software}
	{\copyright \ Copyright by \authorname, July 2021}

@@

\noindent\textbf{NUMBER OF PAGES:} 123

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{circularflow}
		\caption{Streamlines of flow past a stationary circular cylinder at Re = 10, 20, and 40 \citep{chen2021phase}}
		\label{circularflow}
	\end{center}
\end{figure}

@@

This assessment of the state of the practice of LBM software development builds off of prior work on assessing the state of research software development. The previous state of the practice assessments include domains such as Geographic Information Systems \citep{SmithEtAl2018_arXivGIS}, Mesh Generators \citep{SmithEtAl2016}, Oceanographic Software \citep{smith2015state}, Seismology software \citep{SmithEtAl2018}, and statistical software for psychology \citep{SmithEtAl2018_StatSoft}.

@@

A domain analysis consists of systematically identifying and documenting the commonalities, variabilities, and parameters of variation of a software family \citep{Weiss1997}. A software family is defined by \cite{parnas1976design} as “a set of programs whose common properties are so extensive that it is advantageous to study the common properties of the programs before analyzing individual members”.

We added this domain commonality and variability analysis to our original methodology because the first time we did the State of the Practice exercise we found we weren't comparing ``apples to apples". Software packages can have considerable variation, even when the packages appear to be in the same software family. Viewing the ranking exercise as a means for selecting the right tool for a job, functionality is important. A 2D Lattice Boltzmann solver is not a substitute for a 3D Lattice Boltzmann solver when the latter is required. Therefore, this exercise seeks to classify the different software products based on their functionality. Nonfunctional qualities are assessed through other means in our process. For instance, through usability experiments as noted in the \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Methodology.pdf}{Methodology for Assessing the State of the Practice for Domain X} document.

@@

This section lists common features among potential family members. The commonalities are organized using the following abstraction of the system, which can be used to describe all Lattice Boltzmann systems: input information, generate the simulation, output the results. Section \ref{comm_lbm} describes the commonalities for the simulation step. Section \ref{comm_in} highlights the input information that is required for Lattice Boltzmann systems. The next section, Section \ref{comm_out}, shows the common features for the output of Lattice Boltzmann systems, such as the requirement that mesh information be written to files. Although the output information could simply be written to the computer’s memory, in all practical applications it is desirable to have a persistent record of the output that was created.

@@

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & LBS write fluid predictions, such as the output of the transport equation, to memory.\\
		\hline
		\bf Related Variability & \vref{varvisual} \vref{formatoutput} \\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{Variabilities}\label{var_sec}
This section provides a list of characteristics that may vary among family members. As in Section \ref{comm_sec}, the first three subsections on variabilities are organized into the following sublists: Simulation Models, Input and Output. The final subsection lists variabilities that can be characterized as system constraints.

>>>>

\thesistitle
	{\MakeUppercase{\fulltitle}}
	{\MakeUppercase{\authorname}.}
	{Master of Engineering in Computing and Software}
	{\copyright \ Copyright by \authorname, August 2021}

@@

\noindent\textbf{NUMBER OF PAGES:} 125

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{circularflow}
		\caption{Streamlines of flow past a stationary circular cylinder at Reynolds number = 10, 20, and 40 \citep{chen2021phase}}
		\label{circularflow}
	\end{center}
\end{figure}

@@

This assessment of the state of the practice of LBM software development builds off of prior work on assessing the state of research software development. Updates to the methodology used in prior assessments are detailed below. Those assessments include domains such as Geographic Information Systems \citep{SmithEtAl2018_arXivGIS}, Mesh Generators \citep{SmithEtAl2016}, Oceanographic Software \citep{smith2015state}, Seismology software \citep{SmithEtAl2018}, and statistical software for psychology \citep{SmithEtAl2018_StatSoft}.

@@

A domain analysis consists of systematically identifying and documenting the commonalities, variabilities, and parameters of variation of a software family \citep{Weiss1997}. A software family is defined by \cite{parnas1976design} as ``a set of programs whose common properties are so extensive that it is advantageous to study the common properties of the programs before analyzing individual members''.

We added this domain commonality and variability analysis to our original methodology because the first time we did the State of the Practice exercise we found we weren't comparing ``apples to apples". Software packages can have considerable variation, even when the packages appear to be in the same software family. Viewing our final ranking of the software packages as a means for selecting the right tool for a job, functionality is important. A 2D Lattice Boltzmann solver is not a substitute for a 3D Lattice Boltzmann solver when the latter is required. For example, an analysis of a vascular system may require a 3D model to convey all required information to a researcher. This domain analysis helps ensure that the packages that we compare are appropriately similar, and highlights potential differences. This information further helps when analyzing the appropriateness of the final rank of the packages.  This exercise seeks to classify the different software products based on their functionality. Nonfunctional qualities are assessed through other means in our process. For instance, through usability experiments as noted in the \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Methodology.pdf}{Methodology for Assessing the State of the Practice for Domain X} document. This exercise was not part of the methodology of the previous State of the Practice exercise.

@@

This section lists common features among potential family members. These features were chosen after a review of LBM literature and software package specifications. The commonalities are organized using the following abstraction of the system, which can be used to describe all Lattice Boltzmann systems: input information, generate the simulation, output the results. Section \ref{comm_lbm} describes the commonalities for the simulation step. Section \ref{comm_in} highlights the input information that is required for Lattice Boltzmann systems. The next section, Section \ref{comm_out}, shows the common features for the output of Lattice Boltzmann systems, such as the requirement that mesh information be written to files. Although the output information could simply be written to the memory, in all practical applications it is desirable to have a persistent record of the output that was created.

@@

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & LBS write fluid predictions, such as the output of the transport equation, to memory.\\
		\hline
		\bf Related Variability & \vref{varvisual} \vref{formatoutput} \\
		\hline
	\end{tabular}
\end{minipage}\\

\subsection{Variabilities}\label{var_sec}
This section provides a list of characteristics that may vary among family members. These features were chosen after a review of LBM literature and software package specifications. As in Section \ref{comm_sec}, the first three subsections on variabilities are organized into the following sublists: Simulation Models, Input and Output. The final subsection lists variabilities that can be characterized as system constraints.

### 2021-10-06 StateOfPractice/DomainMeasurements/MedImaging-Ao/Empirical Measures Template.tex
Rearrange domain measurement reports to have more consistent naming and locations

\title{Template for Grading Scientific Computing Software} 
\author{Spencer Smith, Adam Lazzarato, Yue Sun, Zheng Zeng,\\ Vasudha Kapil and Jacques Carette}
\date{\today}

\maketitle
\include{RevisedGradingTemplate}

>>>>

\title{Empirical Measures Template} 
\author{Ao Dong}
\date{\today}

\maketitle

The tools for Empirical Measures:
\begin{itemize}
\item \href{https://github.com/tomgi/git_stats}{git\_stats}
\item \href{https://github.com/boyter/scc}{scc}
\end{itemize}

\ad{For now it only contains raw metrics. We'll have to consider how to use them to calculate more meaningful metrics.}

\begin{longtable}{p{16cm}}
  \caption{Grading Template}   \label{table:TemplateFull}\\
  \toprule
  \textbf{Raw Metrics} (Measured via git\_stats)\\
  \midrule
  Number of text-based files. (number)\\
  Number of binary files. (number)\\
  Number of total lines in text-based files. (number)\\
  Number of total lines added to text-based files. (number)\\
  Number of total lines deleted from text-based files. (number)\\
  Number of total commits. (number)\\
Numbers of commits by year in the last 5 years. (Count from as early as possible
if the project is younger than 5 years.) (list of numbers)\\
  Numbers of commits by month in the last 12 months. (list of numbers)\\

  \midrule
  \textbf{Raw Metrics} (Measured via scc)\\
  \midrule
  Number of text-based files. (number)\\
  Number of total lines in text-based files. (number)\\
  Number of code lines in text-based files. (number)\\
  Number of comment lines in text-based files. (number)\\
  Number of blank lines in text-based files. (number)\\

  \midrule
  \textbf{Raw Metrics} (Measured via GitHub API)\\
  \midrule
Numbers of commits, added lines, and deleted lines by author by week.
(2-dimensional list of numbers) \ad{I know we're not likely to measure this.
Just a note that we can get this data. It's only available for GitHub repos, and
I have to test tools for parsing JSON data (e.g. to Excel table).}\\
  \bottomrule

\end{longtable}

### 2021-10-06 StateOfPractice/DomainMeasurements/MedImaging-Ao/Report/01abstract.tex
Rearrange domain measurement reports to have more consistent naming and locations

\begingroup
\setstretch{1.25}
We present a general method to assess the state of the practice for Scientific Computing (SC) software and apply the method to the Medical Imaging (MI) software. This method guided us to select 29 MI software projects from 48 candidates, assess 10 software qualities (\textit{Installability}, \textit{Correctness \& Verifiability}, \textit{Reliability}, \textit{Robustness}, \textit{Usability}, \textit{Maintainability}, \textit{Reusability}, \textit{Understandability}, \textit{Visibility/Transparency}, and \textit{Reproducibility}) by answering 103 questions for each software, and interview eight of the 29 development teams. The results helped us with revealing the current status of MI software development. Based on the quantitative data for the first nine qualities, we ranked the MI software with the Analytic Hierarchy Process (AHP). The top three software products were \textit{3D Slicer}, \textit{ImageJ}, and \textit{OHIF Viewer}, which received high scores for most qualities. \textit{3D Slicer} was among the top two for all nine qualities except \textit{robustness}. By interviewing the developers, we identified three major types of pain points during their development process: i) the lack of resources; ii) the difficulty to balance between four factors: \textit{compatibility}, \textit{maintainability}, \textit{performance}, and \textit{security};
iii) the lack of access to real-world datasets for testing. We collected proven and potential solutions for these problems. The interviews also helped us to understand the status of documentation, project management, and five qualities (\textit{correctness}, \textit{maintainability}, \textit{understandability}, \textit{usability}, and \textit{reproducibility}) in the projects. We summarized the threats and strategies to these qualities. For future SC software development, we proposed recommendations on improving software qualities, dealing with limited resources, choosing a tech stack, and enriching the testing datasets. The recommendations include adopting test-driven development, using continuous integration and continuous delivery (CI/CD), using git and GitHub, maintaining good documents, supporting third-party plugins or extensions, considering web application solutions, and establishing community collaboration in a SC domain.  \newline

>>>>

\begingroup
\setstretch{1.25}
We present a general method to assess the state of the practice for Scientific Computing (SC) software and apply the method to the Medical Imaging (MI) software. This method guided us to select 29 MI software projects from 48 candidates, assess 10 software qualities (\textit{Installability}, \textit{Correctness \& Verifiability}, \textit{Reliability}, \textit{Robustness}, \textit{Usability}, \textit{Maintainability}, \textit{Reusability}, \textit{Understandability}, \textit{Visibility/Transparency}, and \textit{Reproducibility}) by answering 103 questions for each software, and interview eight of the 29 development teams. The results helped us with revealing the current status of MI software development. Based on the quantitative data for the first nine qualities, we ranked the MI software with the Analytic Hierarchy Process (AHP). The top three software products were \textit{3D Slicer}, \textit{ImageJ}, and \textit{OHIF Viewer}, which received high scores for most qualities. \textit{3D Slicer} was among the top two for all nine qualities except \textit{robustness}. By interviewing the developers, we identified three major types of pain points during their development process: i) the lack of resources; ii) the difficulty to balance between four factors: \textit{compatibility}, \textit{maintainability}, \textit{performance}, and \textit{security};
iii) the lack of access to real-world datasets for testing. We collected proven and potential solutions for these problems. The interviews also helped us to understand the status of documentation, project management, and five qualities (\textit{correctness}, \textit{maintainability}, \textit{understandability}, \textit{usability}, and \textit{reproducibility}) in the projects. We summarized the threats and strategies to these qualities. For future SC software development, we proposed recommendations on improving software qualities, dealing with limited resources, choosing a tech stack, and enriching the testing datasets. The recommendations include adopting test-driven development, using continuous integration and continuous delivery (CI/CD), using git and GitHub, maintaining good documentation, supporting third-party plugins or extensions, considering web application solutions, and establishing community collaboration in an SC domain.  \newline

### 2021-10-06 StateOfPractice/DomainMeasurements/MedImaging-Ao/Report/12Background.tex
Rearrange domain measurement reports to have more consistent naming and locations

In this project, the 9 software qualities mentioned above are the criteria ($m = 9$), while 29 software packages ($n = 29$) are compared for each of the $m$ criteria. The software are evaluated with the grading template in Appendix \ref{ap_grading_template} and a subjective score from one to ten is given for each quality for each package. For each quality, for a pair of packages $i$ and $j$, such that $score_i >= score_j$, the difference between two scores is $\mathit{diff_{ij}} = score_i - score_j$. The relationship between $A_{ij} = 1$ and $\mathit{diff_{ij}}$ is as follows:
\begin{itemize}
\item $A_{ij} = 1$ and $\mathit{diff_{ij}} = 0$ when criterion $i$ and criterion $j$ are equally important;
\item $A_{ij}$ increases when $\mathit{diff_{ij}}$ increases;
\item $A_{ij} = 9$ and $\mathit{diff_{ij}} = 9$ when criterion $i$ is extremely more important than criterion $j$.
\end{itemize}
Thus, we approximate the pairwise comparison result of $i$ versus $j$ by the following equation:
\begin{equation}
A_{ij} = min(score_i - score_j + 1, 9)
\end{equation}

>>>>

In this project, the first nine software qualities mentioned in Section \ref{sec_software_quality} are the criteria ($m = 9$), while 29 software packages ($n = 29$) are compared for each of the $m$ criteria. The software are evaluated with the grading template in Appendix \ref{ap_grading_template} and a subjective score from one to ten is given for each quality for each package. For each quality, for a pair of packages $i$ and $j$, such that $score_i >= score_j$, the difference between two scores is $\mathit{diff_{ij}} = score_i - score_j$. The relationship between $A_{ij} = 1$ and $\mathit{diff_{ij}}$ is as follows:
\begin{itemize}
\item $A_{ij} = 1$ and $\mathit{diff_{ij}} = 0$ when criterion $i$ and criterion $j$ are equally important;
\item $A_{ij}$ increases when $\mathit{diff_{ij}}$ increases;
\item $A_{ij} = 9$ and $\mathit{diff_{ij}} = 9$ when criterion $i$ is extremely more important than criterion $j$.
\end{itemize}
Thus, we approximate the pairwise comparison result of $i$ versus $j$ by the following equation:
\begin{equation}
A_{ij} = min(score_i - score_j + 1, 9)
\end{equation}

### 2021-10-06 StateOfPractice/DomainMeasurements/MedImaging-Ao/Report/14MeasurementResults.tex
Rearrange domain measurement reports to have more consistent naming and locations

As discussed in Section \ref{sec_applying_method}, we applied our method to the MI domain. This section shows the summary of the measurement results. The detailed data can be found in the repository \hyperlink{https://data.mendeley.com/datasets/k3pcdvdzj2/1}{https://data.mendeley.com/datasets/k3pcdvdzj2/1}. This section contains part of the answers to \hyperlink{rq5}{RQ5}.

>>>>

As discussed in Section \ref{sec_grading_software}, we use a grading template and a empirical method to measure the selected software. We applied this step to the MI domain (Section \ref{sec_applying_method_grading}). This section shows the summary of the measurement results. The detailed data can be found in the repository \hyperlink{https://data.mendeley.com/datasets/k3pcdvdzj2/1}{https://data.mendeley.com/datasets/k3pcdvdzj2/1}. This section contains part of the answers to \hyperlink{rq5}{RQ5}.

### 2021-10-06 StateOfPractice/DomainMeasurements/MedImaging-Ao/Report/15InterviewsWithDevelopers.tex
Rearrange domain measurement reports to have more consistent naming and locations

Our method involves interviews with developers in the MI domain (Section \ref{sec_applying_method}). We summarize some answers from the interviews in this section. We highlight the answers that are the most informative and interesting in this section, and summarize the rest in Appendix \ref{ap_interview}.

We interviewed nine developers from eight of the 29 MI software projects. The eight projects are \textit{3D Slicer}, \textit{INVESALIUS 3}, \textit{dwv}, \textit{BioImage Suite Web}, \textit{ITK-SNAP}, \textit{MRIcroGL}, \textit{Weasis}, and \textit{OHIF}. We spent about 90 minutes for each interview and asked 20 prepared questions. We also asked following-up questions when we thought it was worth diving deeper. One participant was too busy to have an interview, so they wrote down their answers. The interviewees may have provided multiple answers to each question. Thus, when counting the number of answers, the total result is sometimes larger than nine.

>>>>

The measurement results in Section \ref{ch_results} are based on the information collected by ourselves. Such information is sufficient to measure the projects with reasonable efforts, but incomplete for us to understand the development process more deeply. For example, we usually cannot identify the following information in a project's documents: the pain points during the development, the threats to certain software qualities, and the developers' strategies to address them. We believe interviews with developers can collect the additional information we need. As a result, our method involves interviews with developers in a domain (Section \ref{sec_interview_methods}). We applied this step to the MI domain (Section \ref{sec_apply_to_mi_interviews}).

In this section, we summarize some answers from the interviews. We highlight the answers that are the most informative and interesting in this section, and summarize the rest in Appendix \ref{ap_interview}.

As mentioned in Section \ref{sec_apply_to_mi_interviews}, we contacted all 29 teams. Some of them responded and participated in the interviews. Eventually, we interviewed nine developers from eight of the 29 MI software projects. The eight projects are \textit{3D Slicer}, \textit{INVESALIUS 3}, \textit{dwv}, \textit{BioImage Suite Web}, \textit{ITK-SNAP}, \textit{MRIcroGL}, \textit{Weasis}, and \textit{OHIF}. We spent about 90 minutes for each interview and asked 20 prepared questions. We also asked following-up questions when we thought it was worth diving deeper. One participant was too busy to have an interview, so they wrote down their answers. The interviewees may have provided multiple answers to each question. Thus, when counting the number of answers, the total result is sometimes larger than nine.

### 2021-10-06 StateOfPractice/DomainMeasurements/MedImaging-Ao/Report/16AnswersToResearchQuestions.tex
Rearrange domain measurement reports to have more consistent naming and locations

\section{Threats to Validity}
\label{sec_threats_to_validity}
This section lists all the potential threats to the validity of our research.

\begin{enumerate}
\item We compared nine software qualities for 29 software packages, so we could only spend a limited time on each of them. As a result, our assessments may have missed something relevant.
\item We used the grading template in Appendix \ref{ap_grading_template} to guide our measurements. Our impressions of the software - such as user experience - were factors in deciding some scores. Thus, there is a risk that some scores may be subjective and biased.
\item It was not practical to ask each development team for every piece of information. We collected much information - such as artifacts and funding situations of software - by ourselves. There may be cases that we missed some information.
\item Our ranking is partly based on surface (shallow) measurement, which may not fully reveal the underlying qualities.
\item We interviewed eight teams, which is a good proportion of the 29. However, there is still a risk that they might not well represent the whole MI software community.
\item As mentioned in Section \ref{ch_interview}, one interviewee was too busy to participate in a full interview, so he provided a version of written answers to us. Since we did not have the chance to explain our questions or ask him follow-up questions, there is a possibility of misinterpretation of the questions or answers.
\item As mentioned in Section \ref{sec_result_installability}, we could not install or build \textit{dwv}, \textit{GATE}, and \textit{DICOM Viewer}. We used a deployed online version for \textit{dwv}, a VM version for \textit{GATE}, but no alternative for \textit{DICOM Viewer}. We might underestimate their rank due to uncommon technical issues.
\item Our ranking gave all qualities equal weight, which may not be the case with all users. Thus, it may not represent the popularity of software among users.
\item The number of GitHub stars, watches, and forks are not perfect measures of popularity, but they are what we had available.
\end{enumerate}

>>>>

\section{Threats to Validity}
\label{sec_threats_to_validity}

This section lists all the potential threats to validity in our research. The definitions of common validity are \cite{AmpatzoglouEtAl2019}\cite{ZhouEtAl2016}:
\begin{description}
\item[Construct Validity:] ``Deﬁnes how eﬀectively a test or experiment measures up to its claims. This aspect deals with whether or not the researcher measures what is intended to be measured" \cite{AmpatzoglouEtAl2019}.
\item[Internal Validity:] ``This aspect relates to the examination of causal relations. Internal validity examines whether an experimental treatment/condition makes a diﬀerence or not, and whether there is evidence to support the claim" \cite{AmpatzoglouEtAl2019}.
\item[External Validity:] ``Define the domain to which a study's findings can be
generalized" \cite{ZhouEtAl2016}.
\item[Conclusion Validity:] ``Demonstrate that the operations of a study such as the data collection procedure can be repeated, with the same results" \cite{ZhouEtAl2016}.
\end{description}

\noindent We categorize and present the threats to validity in the following subsections.

\subsection{Threats to Construct Validity}
\begin{itemize}
\item We compared nine software qualities for 29 software packages, so we could only spend a limited time on each of them. As a result, our assessments may have missed something relevant.
\item Our ranking is partly based on surface (shallow) measurement, which may not fully reveal the underlying qualities.
\end{itemize}

\subsection{Threats to Internal Validity}
\begin{itemize}
\item It was not practical to ask each development team for every piece of information. We collected much information - such as artifacts and funding situations of software - by ourselves. There may be cases that we missed some information.
\item As mentioned in Section \ref{ch_interview}, one interviewee was too busy to participate in a full interview, so he provided a version of written answers to us. Since we did not have the chance to explain our questions or ask him follow-up questions, there is a possibility of misinterpretation of the questions or answers.
\item As mentioned in Section \ref{sec_result_installability}, we could not install or build \textit{dwv}, \textit{GATE}, and \textit{DICOM Viewer}. We used a deployed online version for \textit{dwv}, a VM version for \textit{GATE}, but no alternative for \textit{DICOM Viewer}. We might underestimate their rank due to uncommon technical issues.
\end{itemize}

\subsection{Threats to External Validity}
\begin{itemize}
\item We interviewed eight teams, which is a good proportion of the 29. However, there is still a risk that they might not well represent the whole MI software community.
\item Our ranking gave all qualities equal weight, which may not be the case with all users. Thus, it may not represent the popularity of software among users.
\item The number of GitHub stars, watches, and forks are not perfect measures of popularity, but they are what we had available.
\end{itemize}

\subsection{Threats to Conclusion Validity}
\begin{itemize}
\item We used the grading template in Appendix \ref{ap_grading_template} to guide our measurements. Our impressions of the software - such as user experience - were factors in deciding some scores. Thus, there is a risk that some scores may be subjective and biased.
\end{itemize}

### 2021-10-06 StateOfPractice/DomainMeasurements/MedImaging-Ao/Report/18Conclusion.tex
Rearrange domain measurement reports to have more consistent naming and locations

With learnings from this project, we summarized recommendations for the future state of the practice assessments:
\begin{itemize}
    \item we can make the surface measurements less shallow. For example:
    \begin{itemize}
        \item \textit{surface reliability}: our current measurement relies on the processes of installation and getting started tutorials. However, not all software needs installation or has a getting started tutorial. We can design a list of operation steps, perform the same operations with each software, and record any errors.
        \item \textit{surface robustness}: we used damaged images as inputs for this measuring MI software. This process is similar to fuzz testing \cite{enwiki:1039424308}, which is one type of fault injection \cite{enwiki:1039005082}. We may adopt more fault injection methods, and identify tools and libraries to automate this process.
        \item \textit{surface usability}: we can design usability tests and test all software projects with end-users. The end-users can be volunteers and domain experts.
        \item \textit{surface understandability}: our current method does not require understanding the source code. As software engineers, perhaps we can select a small module of each project, read the source code and documentation, try to understand the logic, and score the ease of the process.
    \end{itemize}
	\item we can further automate the measurements on the grading temple in Appendix \ref{ap_grading_template}. For example, with automation scripts and a GitHub API, we may save significant time on retrieving the GitHub metrics;
	\item the grading standard can be more explicit. For example, we can explicitly define scores for each item in the grading temple.
	\item we can improve some interview questions. Some examples are:
	\begin{itemize}
	    \item in \hyperlink{q14}{Q14}, ``Do you think improving this process can tackle the current problem?" is a yes-or-no question, which is not informative enough. As mentioned in Section \ref{sec_contribution_pm}, most interviewees ignored it. We can change it to ``By improving this process, what current problems can be tackled?";
	    \item in \hyperlink{q16}{Q16}, we can ask more details about the modular approach, such as "What principles did you use to divide code into modules? Can you give an example of using the principles?";
	    \item \hyperlink{q17}{Q17} and  \hyperlink{q18}{Q18} should respectively ask \textit{understandability} to developers and \textit{usability} to end-users.
	\end{itemize}
	\item we can better organize the interview questions. Since we use audio conversion tools to transcribe the answers, we should make the transcription easier to read. For example, we can order them together for questions about the five software qualities and compose a similar structure for each.
	\item we can mark the follow-up interview questions with keywords. For example, say ``this is a follow-up question" every time asking one. Thus, we record this sentence in the transcription, and it will be much easier to distinguish the follow-up questions from the 20 designed questions.
\end{itemize}

>>>>

With learnings from this project, we summarized recommendations for the future state of the practice assessments:
\begin{itemize}
    \item we can make the surface measurements less shallow. For example:
    \begin{itemize}
        \item \textit{surface reliability}: our current measurement relies on the processes of installation and getting started tutorials. However, not all software needs installation or has a getting started tutorial. We can design a list of operation steps, perform the same operations with each software, and record any errors.
        \item \textit{surface robustness}: we used damaged images as inputs for this measuring MI software. This process is similar to fuzz testing \cite{enwiki:1039424308}, which is one type of fault injection \cite{enwiki:1039005082}. We may adopt more fault injection methods, and identify tools and libraries to automate this process.
        \item \textit{surface usability}: we can design usability tests and test all software projects with end-users. The end-users can be volunteers and domain experts.
        \item \textit{surface understandability}: our current method does not require understanding the source code. As software engineers, perhaps we can select a small module of each project, read the source code and documentation, try to understand the logic, and score the ease of the process.
    \end{itemize}
	\item we can further automate the measurements on the grading temple in Appendix \ref{ap_grading_template}. For example, with automation scripts and the GitHub API, we may save significant time on retrieving the GitHub metrics. We have started to build a tool for this purpose, with its source code at this repository \hyperlink{https://github.com/smiths/AIMSS/tree/master/StateOfPractice/GitHubMetricsCollector}{https://github.com/smiths/AIMSS/.../GitHubMetricsCollector}. This GitHub Metrics Collector can take GitHub repository links as input, automatically collect metrics from the GitHub API, and record the results. We can improve and use this tool in our future projects;
	\item the grading standard can be more explicit. For example, we can explicitly define scores for each item in the grading temple.
	\item we can improve some interview questions. Some examples are:
	\begin{itemize}
	    \item in \hyperlink{q14}{Q14}, ``Do you think improving this process can tackle the current problem?" is a yes-or-no question, which is not informative enough. As mentioned in Section \ref{sec_contribution_pm}, most interviewees ignored it. We can change it to ``By improving this process, what current problems can be tackled?";
	    \item in \hyperlink{q16}{Q16}, we can ask more details about the modular approach, such as "What principles did you use to divide code into modules? Can you give an example of using the principles?";
	    \item \hyperlink{q17}{Q17} and  \hyperlink{q18}{Q18} should respectively ask \textit{understandability} to developers and \textit{usability} to end-users.
	\end{itemize}
	\item we can better organize the interview questions. Since we use audio conversion tools to transcribe the answers, we should make the transcription easier to read. For example, we can order them together for questions about the five software qualities and compose a similar structure for each.
	\item we can mark the follow-up interview questions with keywords. For example, say ``this is a follow-up question" every time asking one. Thus, we record this sentence in the transcription, and it will be much easier to distinguish the follow-up questions from the 20 designed questions.
\end{itemize}
